Model-based variable selection for regression with highly correlated variables.

### 2014-05-26 www/article13.tex
up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@622 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{lmodern}
\usepackage{subfigure}
\usepackage[table]{xcolor}
 \graphicspath{{figures/}}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
%%\author{Clément THERY, Christophe BIERNACKI, Gaétan LORIDANT}
%\title{Model-based variable selection for regression with highly correlated variables.}

@@

  The idea is that if we know explicitly the correlations, we could use this knowledge to avoid the problem. 
	We use the correlations as new information to reduce the variance without adding any bias.  
  More precisely, we model the correlations with a system of linear sub-regressions for the joint distribution of the covariates to model the structure of the correlations. It helps to define the greatest set of orthogonal covariates to keep the maximum information but with an orthogonality constraint.
Then we can define a marginal model with independent covariates. 
Thus we have an explained variable selection guided by the correlations and it improves interpretation, not only prediction. This marginal model still is the true model but in a different probability space, and OLS still gives an estimator without bias but with a reduced variance for the estimators. The model depends only on independent covariates because it is a marginal model on these covariates.
 This can be viewed as a pretreatment on the dataset that will be followed then by any other tools for estimation and dimension reduction without suffering from correlations. This pretreatment is specifically done to decorrelate the covariates, unlike methods described above. 
The linear structure is obtained by a MCMC algorithm optimizing the penalized likelihood of the joint distribution on the covariates, independently from the response variable. This algorithm is part of the R package \textsc{CorReg} accessible on \textsc{CRAN}. %We only consider strong correlations (i.e. : problematic ones) thus we keep most of the information contained in the dataset. 
 %We will in a second time be able to use the remaining part of the information (sequential approach).

@@

\subsection{A by-product model: marginal regression with decorrelated covariates}
Now we know $P(\boldsymbol{X}_r|\boldsymbol{X}_f,S)$ by the structure of sub-regressions, we are able to define a marginal regression model $P(\boldsymbol{Y}|\boldsymbol{X}_f,S)$ based on the reduced set of independent covariates $\hat{\boldsymbol{\beta}}_f$ without significant information loss. We use the information of the correlations structure to rewrite the true model without bias in the marginal space defined by the independent covariates.
 	\\
Using the partition $\boldsymbol{X}=[\boldsymbol{X}_f,\boldsymbol{X}_r]$ we can rewrite (\ref{regressionsimple}):
	\begin{equation}
			\boldsymbol{Y}_{|\boldsymbol{X}_f,\boldsymbol{X}_r,S}=\boldsymbol{X}_f\boldsymbol{\beta}_f+\boldsymbol{X}_r\boldsymbol{\beta}_r+\boldsymbol{\varepsilon_Y} \label{MainR}
		\end{equation}
		where $\boldsymbol{\beta}=(\boldsymbol{\beta}_f,\boldsymbol{\beta}_r) \in  \mathcal{R}^p$ is the vector of the regression coefficients associated respectively to $\boldsymbol{X}_f$ and $\boldsymbol{I}_n$ the identity matrix. 
We note that (\ref{SR}) and (\ref{MainR}) give also by simple integration on $\boldsymbol{X}_r$ a marginal regression model on $\boldsymbol{Y}$ {\it depending only on uncorrelated covariates $\boldsymbol{X}_f$}:
\begin{eqnarray}
	\boldsymbol{Y}_{|\boldsymbol{X}_f,S}&=&\boldsymbol{X}_f (\boldsymbol{\beta}_f+ \sum_{j \in I_r}\beta_{j}\boldsymbol{\alpha}_j)+  \sum_{j \in I_r}\beta_{j}\boldsymbol{\varepsilon}_j+\boldsymbol{\varepsilon}_Y \label{Trueexpl} \\
	&=&\boldsymbol{X}_f\boldsymbol{\beta}_f^*+\boldsymbol{\varepsilon}_Y^*\label{modexpl}
\end{eqnarray}
 This model is still the true model and OLS estimator will still give an unbiased estimator, but its variance will be reduced by both dimension reduction and decorrelation (variables in $\boldsymbol{X}_f$ are independent so the matrix $\boldsymbol{X}_f'\boldsymbol{X}_f$ will be well-conditioned). So the information given by the structure $S$ allows to reduce the variance without adding bias, by simple marginalization.
\\
Nevertheless, to be able to compare the bias-variance tradeoff, we can see this model as a variable pre-selection independent of the response in $\boldsymbol{Y}_{|\boldsymbol{X}}$.
We note that it is simply a linear regression on some of the original covariates so we only made a pretreatment on the dataset by selecting $\boldsymbol{X}_f$ because of the correlations given by $S$. So we also get the model
\begin{equation}
\boldsymbol{Y}_{|\boldsymbol{X},S}=\boldsymbol{X}\boldsymbol{\beta}^*+\boldsymbol{\varepsilon}_Y^* \textrm{ where }\boldsymbol{\beta}^*=(\boldsymbol{\beta}_f^*,\boldsymbol{\beta}_r^*) \textrm{ and } \boldsymbol{\beta}_r^*=\boldsymbol{0}
\end{equation}
	for which OLS estimator of the coefficients may be biased.

\paragraph{Running example:} $\boldsymbol{Y}_{|\boldsymbol{X}_f}= 2\boldsymbol{x}_1+2\boldsymbol{x}_2+\boldsymbol{x}_4+\boldsymbol{x}_5+\boldsymbol{\varepsilon}_3 +\boldsymbol{\varepsilon}_Y$
\subsection{Strategy of use: pretreatment before classical estimation/selection methods}\label{interpretation}

As a pretreatment, the model allows usage of any method in a second time to estimate $\boldsymbol{\beta}_f^*$, even with variable selection methods like LASSO or a best subset algorithm like stepwise \cite{seber2012linear}. However, we always have $\boldsymbol{X}_r=\boldsymbol{0}$

@@

	\subsection{Illustration of the tradeoff conveyed by the pretreatment}	
	We compare the OLS estimator on $\boldsymbol{X}$ defined in section \ref{sectionOLS} with the estimator obtained by the pretreatment that is $\boldsymbol{X}_f$ selection.

@@

	\subsection{The datasets}	
	Now we have defined the model and the way to obtain it, we can have a look on some numerical results to see if \textsc{CorReg} 	keeps its promises.
	The \textsc{CorReg} package has been tested on simulated datasets. 
Section \ref{compZ} shows the results obtained in terms of $\hat{S}$. Sections \ref{reshatY} and \ref{resrobust} show the results obtained using only \textsc{CorReg}, or \textsc{CorReg} combined with other methods respectively for general case and extreme cases. Figures gives both mean and inter-quartile intervals of the observed Mean Squared Errors (MSE) on a validation sample of $1 000$ individuals. For each simulation,  $p=40$, the $R^2$ of the main regression is $0.4$ and those of the sub-regressions are successively set to $(0.1,0.3,0.5,0.7,0.99)$. Variables in $\boldsymbol{X}_f$ follow Gaussian mixture models of $\lambda=5$ classes which means follow Poisson's law of parameter $\lambda=5$ and which standard deviation is $\lambda$. The $\beta_j$ and the coefficients of the $\boldsymbol{\alpha}_j$ are generated according to the same Poisson law but with a random sign. $\forall j \in I_r, p_1^j=2$ (sub-regressions of length 2) and we have $p_r=16$ sub-regressions. The datasets were then scaled so that covariates $X_r$ don't have a greater variance or mean.
	We used \textsc{Rmixmod} to estimate the densities of each covariate. For each configuration, the MCMC walk was launched on $10$ initial structures with a maximum of 1 000 steps each time.
	When $n<p$, a frequently used method is the Moore-Penrose generalized inverse \cite{katsikis2008fast}, thus OLS can obtain some results even with $n<p$. %(see tables \ref{YXlinOLS} and \ref{YX2linOLS} ).
	When using penalized estimators for selection, a last Ordinary Least Square step is added to improve estimation because penalisation is made to select variables but also shrinks remaining coefficients. This last step allows to keep the benefits of shrinkage (variable selection) without any impact on remaining coefficients (see \cite{SAM10088}) and is applied for both classical and marginal model.
	We compare different methods with and without CorReg as a pretreatment. All the results are provided by the CorReg package. In the following figures, the thickness represent various values of $n$, the thicker the greater, in $(30,50,100,400)$ so we start from $n<p$.
		\subsection{Finding the structure}
		\subsubsection{How to evaluate found structure?}
			The first criterion is $\psi(\boldsymbol{X},S)$ which is maximized in the MCMC. But in our case, it is estimated by the likelihood (see (\ref{approxBIC}))whose value don't have any intrinsic meaning. To show how far the found structure is from the true one in terms of $S$ we define some indicators to compare the true model $S$ and the found $\hat{S}$:
			\begin{itemize}
				\item $TL$ (True left) : the number of found dependent variables that really are dependent $TL=|I_r\cap \hat{I}_r|$ 
				\item $WL$ (Wrong left) : the number of found dependent variables that are not dependent $WL=|\hat{I}_r|-TL$
				\item $ML$ (Missing left) : the number of really dependent variables not found $ML=|I_r|-TL$
				\item $\Delta p_r$ : the gap between the number of sub-regression in both model : $\Delta p_r=|I_r|-|\hat{I}_r|$. The sign defines if $\hat{S}$ is too complex or too simple.
				%\item $\Delta compl$ : the difference in complexity between both model : $\Delta compl=\sum_{j \in p_r}p_f^j-\sum_{j \in \hat{p}_r}\hat{p}_f^j$
			\end{itemize}

		\subsubsection{Results on $S$}	\label{compZ}
Here we just take a look at $TL$ and $WL$, that fully describe the quality of the variable selection that will be made in the marginal model. $ML$ and $\Delta p_r$ can be deduced knowing the value of $p_r$ (16 in these cases).
\begin{figure}[h!] \label{reshatZ}
	\begin{minipage}[l]{.48\linewidth}
			\includegraphics[height=180px,width=245px]{figures/res_article/BIC_p2.png} 
			\caption{Quality of the subregressions found with classical $BIC$ criterion}
	\end{minipage} \
   \begin{minipage}[r]{.48\linewidth}
			\includegraphics[height=180px,width=240px]{figures/res_article/BICSTAR_P2.png} 
			\caption{Quality of the subregressions found with our $BIC_+$ criterion} 
   \end{minipage}
\end{figure}
We can clearly observe that $BIC_+$ find less sub-regressions when $R^2$ is small and give less wrong sub-regressions than $BIC$ for every $R^2$ but when the strength of the sub-regression increases, $BIC_+$ find as much good sub-regressions as the $BIC$ so the objective is reached. We found the sub-regression only when they are significant and we reduce the noise.

\clearpage
\subsection{Results on prediction}\label{reshatY}

@@

 Figure \ref{toutOLS} (left) shows that CorReg improves the prediction power of OLS in a significant way for small values of $n$ and/or significant linear structures. This advantage then shrinks when $n$ explodes because the matrix to invert become well-conditioned and the true model does depend on all covariates (not allowed in the marginal model). We also see that (Figure \ref{toutOLS} right) the model provided by CorReg is more parsimonious and that for small values of $n$ and weak sub-regressions, the number of found sub-regressions is reduced so the marginal model tends to keep more covariates.
%\caption{OLS and OLS combined with constrained \textsc{CorReg}. $\boldsymbol{Y}$  depends on all variables in $\boldsymbol{X}$. \textsc{CorReg} logically wins. When $n<p$ the dataset was reduced to $p=n$ automatically by a $QR$ decomposition as the lm function of R does. Without selection, all models have min$(n,p)$ non-zero coefficients.} \label{YXlinOLS}

@@

\begin{figure}[h!]
	\subfigure[MSE on a validation subset]{
			\includegraphics[height=180px,width=245px]{figures/res_article/stepwise_tout_MSE_NB.png} 
	} \quad
   	\subfigure[Complexity]{
			\includegraphics[height=180px,width=240px]{figures/res_article/stepwise_tout_compl_NB.png} 
	}
	\caption{Comparison of stepwise (dotted) and CorReg + stepwise (plain) when $Y$ depends on all covariates. Thickness represents $n=30,50,100,400$.}\label{toutstepwise}
\end{figure}
Figures \ref{toutlar}, \ref{toutelast} and \ref{toutstepwise} show that CorReg used as a pretreatment improves the results obtained by variable selection methods and tends to give a more parsimonious model. This is remarkable because the true model depends on all covariates, so it shows that other variable selection methods are really penalized by the correlations between the covariates.

 \begin{figure}[h!]
	\subfigure[MSE on a validation subset]{
			\includegraphics[height=180px,width=245px]{figures/res_article/ridge_tout_MSE_NB.png} 
	} \quad
   	\subfigure[Complexity]{
			\includegraphics[height=180px,width=240px]{figures/res_article/ridge_tout_compl_NB.png} 
	}
	\caption{Comparison of ridge (dotted) and CorReg + ridge (plain) when $Y$ depends on all covariates. Thickness represents $n=30,50,100,400$.}\label{toutridge}
\end{figure}
Figure \ref{toutridge} shows that the ridge regression is efficient in prediction when confronted to correlated covariates. It is directly made to improve the conditioning and keeps all the covariates (as the true model) so it logically gives better predictions than CorReg which delete some covariates. But we notice that CorReg pretreatment before the ridge regression gives MSE that are really near form those from the ridge regression alone (inter-quartile intervals are essentially mingled) and with a parsimonious model.
Ridge regression alone gives a full model (40 covariates even with only 30 individuals) and will give models too complex to be interpreted. A model with 40 covariates is already difficult to interpret and it get worse when $p$ rises. So even the ridge regression in its most favorable case (True model depending on all the covariates) takes benefits (for interpretation) form the CorReg pretreatment.
\clearpage

@@

\begin{figure}[h!]
	\subfigure[MSE on a validation subset]{
			\includegraphics[height=180px,width=245px]{figures/res_article/lar_X1_MSE_NB.png} 
	} \quad
   	\subfigure[Complexity]{
			\includegraphics[height=180px,width=240px]{figures/res_article/lar_X1_compl_NB.png} 
	}
	\caption{Comparison of LASSO (dotted) and CorReg + LASSO (plain) when $Y$ depends on $X_f$ only. Thickness represents $n=30,50,100,400$.}\label{X1lasso}
\end{figure}
Figures \ref{X1OLS} and \ref{X1lasso} lead to the same comparison. Even if the true model needs variable selection and depends only on independent covariates, if the dataset contained correlated but irrelevant covariates then classical variable selection methods gain to be associated with a pretreatment by CorReg.

@@

	\subsubsection{$\boldsymbol{Y}$ depends only on covariates in $\boldsymbol{X_r}$ (worst case for us)}	 \label{tableMSEsimgauche}
We now try the method with a response depending only on variables in $\boldsymbol{X}_r$. The datasets used here were still the same as for Figure \ref{reshatZ}.
Depending only on $\boldsymbol{X}_r$ implies sparsity and impossibility to obtain the true model when using the true structure.

 \begin{figure}[h!]
	\begin{minipage}[l]{.48\linewidth}
			\includegraphics[height=180px,width=245px]{figures/res_article/OLS_X2_MSE_NB.png} 
			\caption{Comparison of the MSE between OLS and CorReg+OLS}
	\end{minipage} \
   \begin{minipage}[r]{.48\linewidth}
			\includegraphics[height=180px,width=240px]{figures/res_article/OLS_X2_compl_NB.png} 
			\caption{Comparison of the complexities between OLS and CorReg+OLS} 
   \end{minipage}
\end{figure}
\textsc{CorReg} is still better than OLS for strong correlations and limited values of $n$. 
 \begin{figure}[h!]
	\begin{minipage}[l]{.48\linewidth}
			\includegraphics[height=180px,width=245px]{figures/res_article/lar_X2_MSE_NB.png} 
			\caption{Comparison of the MSE between LASSO and CorReg+LASSO}
	\end{minipage} \
   \begin{minipage}[r]{.48\linewidth}
			\includegraphics[height=180px,width=240px]{figures/res_article/lar_X2_compl_NB.png} 
			\caption{Comparison of the complexities between LASSO and CorReg+LASSO} 
   \end{minipage}
\end{figure}

\clearpage
\subsubsection{non-linear case}

@@

 \begin{figure}[h!] \label{resnonlin}
	\begin{minipage}[l]{.48\linewidth}
			\includegraphics[height=180px,width=245px]{figures/res_article/robust_S.png} 
			\caption{Quality of the structure found when the paramater $a$ increases}
	\end{minipage} \
   \begin{minipage}[r]{.48\linewidth}
			\includegraphics[height=180px,width=240px]{figures/res_article/robust_MSE.png} 
			\caption{MSE on the main regression.}
   \end{minipage}
\end{figure}

	\clearpage	
\section{Numerical results on real datasets} \label{sectionrealcase}
\subsection{Quality case study} \label{sectionexfos}
This work takes place in steel industry context, with quality oriented objective : to understand and prevent quality problems on finished product, knowing the whole process. The correlations are strong here (many parameters of the whole process without any a priori and highly correlated because of physical laws, process rules, {\it etc.}).

We have :
		\begin{itemize}
			\item a quality parameter (confidential) as response variable,
			\item 205 variables from the whole process to explain it.
			\item The stakes : a hundred euros per ton (for information: Dunkerque's  site aims to produce up to 7.5 millions tons a year)
		\end{itemize}

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{lmodern}
\usepackage{subfigure}
\usepackage{placeins}
\usepackage[table]{xcolor}
 \graphicspath{{figures/}}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
%%\author{Clément THERY, Christophe BIERNACKI, Gaétan LORIDANT}
%\title{Model-based variable selection for regression with highly correlated variables.}

@@

  The idea is that if we know explicitly the correlations, we could use this knowledge to avoid the problem. 
	We use the correlations as new information to reduce the variance without adding any bias.  
  More precisely, we model the correlations with a system of linear sub-regressions for the joint distribution of the covariates to model the structure of the correlations. It helps to define the greatest set of orthogonal covariates to keep the maximum information but with an orthogonality constraint.
Then we can define a marginal model with independent covariates. 
Thus we have an explained variable selection guided by the correlations and it improves interpretation, not only prediction. This marginal model still is the true model but in a different probability space, and OLS still gives an estimator without bias but with a reduced variance for the estimators. The model depends only on independent covariates because it is a marginal model on these covariates.
 This can be viewed as a pre-treatment on the dataset that will be followed then by any other tools for estimation and dimension reduction without suffering from correlations. This pre-treatment is specifically done to decorrelate the covariates, unlike methods described above. 
The linear structure is obtained by a MCMC algorithm optimizing the penalized likelihood of the joint distribution on the covariates, independently from the response variable. This algorithm is part of the R package \textsc{CorReg} accessible on \textsc{CRAN}. %We only consider strong correlations (i.e. : problematic ones) thus we keep most of the information contained in the dataset. 
 %We will in a second time be able to use the remaining part of the information (sequential approach).

@@

\subsection{A by-product model: marginal regression with decorrelated covariates}
Now we know $P(\boldsymbol{X}_r|\boldsymbol{X}_f,S)$ by the structure of sub-regressions, we are able to define a marginal regression model $P(\boldsymbol{Y}|\boldsymbol{X}_f,S)$ based on the reduced set of independent covariates $\hat{\boldsymbol{\beta}}_f$ without significant information loss. We use the information of the correlations structure to rewrite the true model without bias in the marginal space defined by the independent covariates.
 	\\
Using the partition $\boldsymbol{X}=[\boldsymbol{X}_f,\boldsymbol{X}_r]$ we can rewrite (\ref{regressionsimple}):
	\begin{equation}
			\boldsymbol{Y}_{|\boldsymbol{X}_f,\boldsymbol{X}_r,S}=\boldsymbol{X}_f\boldsymbol{\beta}_f+\boldsymbol{X}_r\boldsymbol{\beta}_r+\boldsymbol{\varepsilon_Y} \label{MainR}
		\end{equation}
		where $\boldsymbol{\beta}=(\boldsymbol{\beta}_f,\boldsymbol{\beta}_r) \in  \mathcal{R}^p$ is the vector of the regression coefficients associated respectively to $\boldsymbol{X}_f$ and $\boldsymbol{I}_n$ the identity matrix. 
We note that (\ref{SR}) and (\ref{MainR}) give also by simple integration on $\boldsymbol{X}_r$ a marginal regression model on $\boldsymbol{Y}$ {\it depending only on uncorrelated covariates $\boldsymbol{X}_f$}:
\begin{eqnarray}
	\boldsymbol{Y}_{|\boldsymbol{X}_f,S}&=&\boldsymbol{X}_f (\boldsymbol{\beta}_f+ \sum_{j \in I_r}\beta_{j}\boldsymbol{\alpha}_j)+  \sum_{j \in I_r}\beta_{j}\boldsymbol{\varepsilon}_j+\boldsymbol{\varepsilon}_Y \label{Trueexpl} \\
	&=&\boldsymbol{X}_f\boldsymbol{\beta}_f^*+\boldsymbol{\varepsilon}_Y^*\label{modexpl}
\end{eqnarray}
 This model is still the true model and OLS estimator will still give an unbiased estimator, but its variance will be reduced by both dimension reduction and decorrelation (variables in $\boldsymbol{X}_f$ are independent so the matrix $\boldsymbol{X}_f'\boldsymbol{X}_f$ will be well-conditioned). So the information given by the structure $S$ allows to reduce the variance without adding bias, by simple marginalization.
\\
Nevertheless, to be able to compare the bias-variance tradeoff, we can see this model as a variable pre-selection independent of the response in $\boldsymbol{Y}_{|\boldsymbol{X}}$.
We note that it is simply a linear regression on some of the original covariates so we only made a pre-treatment on the dataset by selecting $\boldsymbol{X}_f$ because of the correlations given by $S$. So we also get the model
\begin{equation}
\boldsymbol{Y}_{|\boldsymbol{X},S}=\boldsymbol{X}\boldsymbol{\beta}^*+\boldsymbol{\varepsilon}_Y^* \textrm{ where }\boldsymbol{\beta}^*=(\boldsymbol{\beta}_f^*,\boldsymbol{\beta}_r^*) \textrm{ and } \boldsymbol{\beta}_r^*=\boldsymbol{0}
\end{equation}
	for which OLS estimator of the coefficients may be biased.

\paragraph{Running example:} $\boldsymbol{Y}_{|\boldsymbol{X}_f}= 2\boldsymbol{x}_1+2\boldsymbol{x}_2+\boldsymbol{x}_4+\boldsymbol{x}_5+\boldsymbol{\varepsilon}_3 +\boldsymbol{\varepsilon}_Y$
\subsection{Strategy of use: pre-treatment before classical estimation/selection methods}\label{interpretation}

As a pre-treatment, the model allows usage of any method in a second time to estimate $\boldsymbol{\beta}_f^*$, even with variable selection methods like LASSO or a best subset algorithm like stepwise \cite{seber2012linear}. However, we always have $\boldsymbol{X}_r=\boldsymbol{0}$

@@

	\subsection{Illustration of the tradeoff conveyed by the pre-treatment}	
	We compare the OLS estimator on $\boldsymbol{X}$ defined in section \ref{sectionOLS} with the estimator obtained by the pre-treatment that is $\boldsymbol{X}_f$ selection.

@@

	\subsection{The datasets}	
	Now we have defined the model and the way to obtain it, we can have a look on some numerical results to see if \textsc{CorReg} 	keeps its promises.
	The \textsc{CorReg} package has been tested on simulated datasets. 
Section \ref{compZ} shows the results obtained in terms of $\hat{S}$. Sections \ref{reshatY} and \ref{resrobust} show the results obtained using only \textsc{CorReg}, or \textsc{CorReg} combined with other methods respectively for general case and extreme cases. Figures gives both mean and inter-quartile intervals of the observed Mean Squared Errors (MSE) on a validation sample of $1 000$ individuals. For each simulation,  $p=40$, the $R^2$ of the main regression is $0.4$ and those of the sub-regressions are successively set to $(0.1,0.3,0.5,0.7,0.99)$. Variables in $\boldsymbol{X}_f$ follow Gaussian mixture models of $\lambda=5$ classes which means follow Poisson's law of parameter $\lambda=5$ and which standard deviation is $\lambda$. The $\beta_j$ and the coefficients of the $\boldsymbol{\alpha}_j$ are generated according to the same Poisson law but with a random sign. $\forall j \in I_r, p_1^j=2$ (sub-regressions of length 2) and we have $p_r=16$ sub-regressions. The datasets were then scaled so that covariates $X_r$ don't have a greater variance or mean.
	We used \textsc{Rmixmod} to estimate the densities of each covariate. For each configuration, the MCMC walk was launched on $10$ initial structures with a maximum of 1 000 steps each time.
	When $n<p$, a frequently used method is the Moore-Penrose generalized inverse \cite{katsikis2008fast}, thus OLS can obtain some results even with $n<p$. %(see tables \ref{YXlinOLS} and \ref{YX2linOLS} ).
	When using penalized estimators for selection, a last Ordinary Least Square step is added to improve estimation because penalisation is made to select variables but also shrinks remaining coefficients. This last step allows to keep the benefits of shrinkage (variable selection) without any impact on remaining coefficients (see \cite{SAM10088}) and is applied for both classical and marginal model.
	We compare different methods with and without CorReg as a pre-treatment. All the results are provided by the CorReg package. In the following figures, the thickness represent various values of $n$, the thicker the greater, in $(30,50,100,400)$ so we start from $n<p$.
		\subsection{Finding the structure}
		\subsubsection{How to evaluate found structure?}
			The first criterion is $\psi(\boldsymbol{X},S)$ which is maximized in the MCMC. But in our case, it is estimated by the likelihood (see (\ref{approxBIC}))whose value don't have any intrinsic meaning. To show how far the found structure is from the true one in terms of $S$ we define some indicators to compare the true model $S$ and the found $\hat{S}$:
			\begin{itemize}
				\item $TL$ (True left) : the number of found dependent variables that really are dependent $TL=|I_r\cap \hat{I}_r|$ 
				\item $WL$ (Wrong left) : the number of found dependent variables that are not dependent $WL=|\hat{I}_r|-TL$
				\item $ML$ (Missing left) : the number of really dependent variables not found $ML=|I_r|-TL$
				\item $\Delta p_r$ : the gap between the number of sub-regression in both model : $\Delta p_r=|I_r|-|\hat{I}_r|$. The sign defines if $\hat{S}$ is too complex or too simple.
				%\item $\Delta compl$ : the difference in complexity between both model : $\Delta compl=\sum_{j \in p_r}p_f^j-\sum_{j \in \hat{p}_r}\hat{p}_f^j$
			\end{itemize}

		\subsubsection{Results on $S$}	\label{compZ}
Here we just take a look at $TL$ and $WL$, that fully describe the quality of the variable selection that will be made in the marginal model. $ML$ and $\Delta p_r$ can be deduced knowing the value of $p_r$ (16 in these cases).
\begin{figure}[h!]
	\subfigure[with $BIC$ criterion]{
			\includegraphics[height=180px,width=245px]{figures/res_article/BIC_p2.png} 
	} \quad
   	\subfigure[with $BIC_+$ criterion]{
			\includegraphics[height=180px,width=240px]{figures/res_article/BICSTAR_P2.png} 
	}
	\caption{Quality of the found subregressions (dotted = True Left, plain = Wrong Left). Thickness represents $n=30,50,100,400$.}\label{reshatZ}
\end{figure}

We can clearly observe that $BIC_+$ find less sub-regressions when $R^2$ is small and give less wrong sub-regressions than $BIC$ for every $R^2$ but when the strength of the sub-regression increases, $BIC_+$ find as much good sub-regressions as the $BIC$ so the objective is reached. We found the sub-regression only when they are significant and we reduce the noise.

\FloatBarrier
\subsection{Results on prediction}\label{reshatY}

@@

 Figure \ref{toutOLS} (a) shows that CorReg improves the prediction power of OLS in a significant way for small values of $n$ and/or significant linear structures. This advantage then shrinks when $n$ explodes because the matrix to invert become well-conditioned and the true model does depend on all covariates (not allowed in the marginal model). We also see that (Figure \ref{toutOLS} (b)) the model provided by CorReg is more parsimonious and that for small values of $n$ and weak sub-regressions, the number of found sub-regressions is reduced so the marginal model tends to keep more covariates.
%\caption{OLS and OLS combined with constrained \textsc{CorReg}. $\boldsymbol{Y}$  depends on all variables in $\boldsymbol{X}$. \textsc{CorReg} logically wins. When $n<p$ the dataset was reduced to $p=n$ automatically by a $QR$ decomposition as the lm function of R does. Without selection, all models have min$(n,p)$ non-zero coefficients.} \label{YXlinOLS}

@@

\begin{figure}[h!]
	\subfigure[MSE on a validation subset]{
			\includegraphics[height=180px,width=245px]{figures/res_article/stepwise_tout_MSE_NB.png} 
	} \quad
   	\subfigure[Complexity]{
			\includegraphics[height=180px,width=240px]{figures/res_article/stepwise_tout_compl_NB.png} 
	}
	\caption{Comparison of stepwise (dotted) and CorReg + stepwise (plain) when $Y$ depends on all covariates. Thickness represents $n=30,50,100,400$.}\label{toutstepwise}
\end{figure}
Figures \ref{toutlar}, \ref{toutelast} and \ref{toutstepwise} show that CorReg used as a pre-treatment improves the results obtained by variable selection methods and tends to give a more parsimonious model. This is remarkable because the true model depends on all covariates, so it shows that other variable selection methods are really penalized by the correlations between the covariates.

 \begin{figure}[h!]
	\subfigure[MSE on a validation subset]{
			\includegraphics[height=180px,width=245px]{figures/res_article/ridge_tout_MSE_NB.png} 
	} \quad
   	\subfigure[Complexity]{
			\includegraphics[height=180px,width=240px]{figures/res_article/ridge_tout_compl_NB.png} 
	}
	\caption{Comparison of ridge (dotted) and CorReg + ridge (plain) when $Y$ depends on all covariates. Thickness represents $n=30,50,100,400$.}\label{toutridge}
\end{figure}
Figure \ref{toutridge} shows that the ridge regression is efficient in prediction when confronted to correlated covariates. It is directly made to improve the conditioning and keeps all the covariates (as the true model) so it logically gives better predictions than CorReg which delete some covariates. But we notice that CorReg pre-treatment before the ridge regression gives MSE that are really near form those from the ridge regression alone (inter-quartile intervals are essentially mingled) and with a parsimonious model.
Ridge regression alone gives a full model (40 covariates even with only 30 individuals) and will give models too complex to be interpreted. A model with 40 covariates is already difficult to interpret and it get worse when $p$ rises. So even the ridge regression in its most favorable case (True model depending on all the covariates) takes benefits (for interpretation) form the CorReg pre-treatment.
\FloatBarrier

@@

\begin{figure}[h!]
	\subfigure[MSE on a validation subset]{
			\includegraphics[height=180px,width=245px]{figures/res_article/lar_X1_MSE_NB.png} 
	} \quad
   	\subfigure[Complexity]{
			\includegraphics[height=180px,width=240px]{figures/res_article/lar_X1_compl_NB.png} 
	}
	\caption{Comparison of LASSO (dotted) and CorReg + LASSO (plain) when $Y$ depends on $X_f$ only. Thickness represents $n=30,50,100,400$.}\label{X1lasso}
\end{figure}
Figures \ref{X1OLS} and \ref{X1lasso} lead to the same comparison. Even if the true model needs variable selection and depends only on independent covariates, if the dataset contained correlated but irrelevant covariates then classical variable selection methods gain to be associated with a pre-treatment by CorReg.

@@

\FloatBarrier
	\subsubsection{$\boldsymbol{Y}$ depends only on covariates in $\boldsymbol{X_r}$ (worst case for us)}	 \label{tableMSEsimgauche}
We now try the method with a response depending only on variables in $\boldsymbol{X}_r$. The datasets used here were still the same as for Figure \ref{reshatZ}.
Depending only on $\boldsymbol{X}_r$ implies sparsity and impossibility to obtain the true model when using the true structure. 
\begin{figure}[h!]
	\subfigure[MSE on a validation subset]{
			\includegraphics[height=180px,width=245px]{figures/res_article/OLS_X2_MSE_NB.png} 
	} \quad
   	\subfigure[Complexity]{
			\includegraphics[height=180px,width=240px]{figures/res_article/OLS_X2_compl_NB.png} 
	}
	\caption{Comparison of OLS (dotted) and CorReg + OLS (plain) when $Y$ depends on $X_r$ only. Thickness represents $n=30,50,100,400$.}\label{X2OLS}
\end{figure}

Figure \ref{X2OLS} reveals that \textsc{CorReg} is still better than OLS for strong correlations and limited values of $n$. When $n$ rises, we found the sub-regression and then delete relevant covariates so CorReg does not improve the results and increases the MSE. but for strong correlations, the error shrinks as the model tends to be less identifiable and switching variables is not a problem anymore even with large values of $n$.

\begin{figure}[h!]
	\subfigure[MSE on a validation subset]{
			\includegraphics[height=180px,width=245px]{figures/res_article/lar_X2_MSE_NB.png} 
	} \quad
   	\subfigure[Complexity]{
			\includegraphics[height=180px,width=240px]{figures/res_article/lar_X2_compl_NB.png} 
	}
	\caption{Comparison of LASSO (dotted) and CorReg + LASSO (plain) when $Y$ depends on $X_r$ only. Thickness represents $n=30,50,100,400$.}\label{X2LASSO}
\end{figure}
Figure \ref{X2LASSO} shows that LASSO naturally tends to keep $\boldsymbol{X_r}$ and thus is better in such a true model. So CorReg is not always the better solution and it is recommended to compare classical and marginal model. This model choice is only between two models so it avoids multiple tests issues and computational cost explosion. We suggest to always compute the complete model and the marginal one and then to compare them with the more pertinent criterion (AIC, cross-validation, validation sample, {\it etc. }) according to the context (size of the datasets for example).

It is notable that the structure does not depend on $\boldsymbol{Y}$ so it can be used for several studies and has an intrinsic value for interpretation even when the marginal model is not kept after confrontation with the classical one. CorReg is both a pre-study and a pre-treatment

\FloatBarrier
\subsubsection{non-linear case}

@@

 \begin{figure}[h!] 
	\begin{minipage}[l]{.48\linewidth}
			\includegraphics[height=180px,width=245px]{figures/res_article/robust_S.png} 
			\caption{Frequency of true $\boldsymbol{X}_r$ found (plain)   when the paramater $a$ increases}\label{resnonlin}
	\end{minipage} \
   \begin{minipage}[r]{.48\linewidth}
			\includegraphics[height=180px,width=240px]{figures/res_article/robust_MSE.png} \label{MSEnonlin}
			\caption{MSE on the main regression for OLS(thick) and LASSO (thin) used both with (plain) or without CorReg (dotted).}
   \end{minipage}
\end{figure}
Figure \ref{MSEnonlin} illustrates the advantage of using CorReg even with non-linear structures. Figure \ref{resnonlin} shows that the MCMC have more difficulties to find a linear structure as the non-linear part of the sub-regression increases but the model is quite robust (efficient for small values of $a$)

	\FloatBarrier	
\section{Numerical results on real datasets} \label{sectionrealcase}
\subsection{Quality case study} \label{sectionexfos}
This work takes place in steel industry context, with quality oriented objective : to understand and prevent quality problems on finished product, knowing the whole process. The correlations are strong here (many parameters of the whole process without any a priori and highly correlated because of physical laws, process rules, {\it etc.}).

We have :
		\begin{itemize}
			\item a quality parameter (confidential) as response variable,
			\item 205 variables from the whole process to explain it.
		\end{itemize}
